Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-08 paper.tex
Modified figure 7 caption

\begin{figure}[h]
  \centering
  \begin{subfigure}{.2375\textwidth}
    \includegraphics[width=4cm]{method-a.pdf}\\
    \subcaption{} % 4 words max
    \label{fig:method-a}
  \end{subfigure}%
  \begin{subfigure}{.2375\textwidth}
    \includegraphics[width=4cm]{method-b.pdf}\\
    \subcaption{} % 4words max
    \label{fig:method-b}
  \end{subfigure}%
  \vspace{5.0pt}% To create a bit of vertical space between the 2 figure captions
  \label{fig:method}
  \caption{Spatial aggregation based on provincial administrative boundaries diagrammatically represented. (a) Individual data records are depicted geographically with arrows connecting origins to their respective destinations. (b) The result of aggregation is a set of weighted connections between provinces.}
\end{figure}

Next, the data is aggregated so that province level flow patterns are emphasized.
\cref{fig:method} provides a diagrammatic representation of spatial aggregation on the basis of provincial administrative boundaries.
To compare the volume of flow between rural provincial areas and urbanized zones, train stations in major cities were aggregated into seperate groups. 
Simiarly, stations located outside of Belgium were aggregated to distinct group. 
A diagrammatic breakdown is depicted in \cref{fig:method-c} where color and shape is used to demarcate each group.
The following types of flows are observable from the outcome of aggregation:

@@

\begin{figure*}
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=13cm]{weekdays_morning.pdf}\\
    \subcaption{Weekdays} % 4 words max
    \label{fig:weekdays_morning}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=13cm]{weekends_morning.pdf}\\
    \subcaption{Weekends} % 4words max
    \label{fig:weekends_morning}
  \end{subfigure}
  \vspace{5.0pt}% To create a bit of vertical space between the 2 figure captions
  \label{fig:mornings}
  \caption{Comparison of morning rush hour travel flows on weekdays and weekends.}
\end{figure*}

\begin{figure*}[t]
\begin{tabular}{ccc}
  \includegraphics[width=.33\textwidth]{wd-brussels.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-antwerp.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-gent.pdf}\\
  (a) Brussels City&(b) Antwerp City&(c) Gent\\[6pt]
  \includegraphics[width=.33\textwidth]{wd-leuven.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-liege.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-mons.pdf}\\ 
  (d) Leuven&(e) Liege City&(f) Mons\\
\end{tabular}
\label{fig:cities}
\centering
\caption{Comparison of morning rush hour travel flows on weekdays originating from or towards six major cities in Belgium.}
\end{figure*}

>>>>

\begin{figure}[h]
  \centering
  \begin{subfigure}{.2375\textwidth}
    \includegraphics[width=4cm]{method-a.pdf}\\
    \subcaption{} % 4 words max
    \label{fig:method-a}
  \end{subfigure}%
  \begin{subfigure}{.2375\textwidth}
    \includegraphics[width=4cm]{method-b.pdf}\\
    \subcaption{} % 4words max
    \label{fig:method-b}
  \end{subfigure}%
  \vspace{5.0pt}% To create a bit of vertical space between the 2 figure captions
  \caption{Spatial aggregation based on provincial administrative boundaries diagrammatically represented. (a) Individual data records are depicted geographically with arrows connecting origins to their respective destinations. (b) The result of aggregation is a set of weighted connections between provinces.}
  \label{fig:method-ab}
\end{figure}

Next, the data is aggregated so that province level flow patterns are emphasized.
\cref{fig:method-ab} provides a diagrammatic representation of spatial aggregation on the basis of provincial administrative boundaries.
To compare the volume of flow between rural provincial areas and urbanized zones, train stations in major cities were aggregated into seperate groups. 
Simiarly, stations located outside of Belgium were aggregated to distinct group. 
A diagrammatic breakdown is depicted in \cref{fig:method-c} where color and shape is used to demarcate each group.
The following types of flows are observable from the outcome of aggregation:

@@

\begin{figure*}
  \centering
  \begin{subfigure}{.95\textwidth}
    \centering
    \includegraphics[width=13cm]{weekdays_morning.pdf}\\
    \subcaption{Weekdays} % 4 words max
    \label{fig:weekdays_morning}
  \end{subfigure}
  \begin{subfigure}{.95\textwidth}
    \centering
    \includegraphics[width=13cm]{weekends_morning.pdf}\\
    \subcaption{Weekends} % 4words max
    \label{fig:weekends_morning}
  \end{subfigure}
  \vspace{5.0pt}% To create a bit of vertical space between the 2 figure captions
  \caption{Comparison of morning rush hour travel flows on weekdays and weekends.}
  \label{fig:mornings}
\end{figure*}

\begin{figure*}[t]
\begin{tabular}{ccc}
  \includegraphics[width=.33\textwidth]{wd-brussels.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-antwerp.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-gent.pdf}\\
  (a) Brussels City&(b) Antwerp City&(c) Gent\\[6pt]
  \includegraphics[width=.33\textwidth]{wd-leuven.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-liege.pdf}& 
  \includegraphics[width=.33\textwidth]{wd-mons.pdf}\\ 
  (d) Leuven&(e) Liege City&(f) Mons\\
\end{tabular}
\label{fig:cities}
\centering
\caption{Comparison of morning rush hour travel flows on weekdays originating from or destined for six major cities in Belgium.}
\end{figure*}
